The paradox of Machine Translation base on Sentiment Analysis polarity: using Metamorphic Testing

### 2019-02-01 icse/paper.tex
backup 01.02 12:32

\section{Introduction}
Most people encounter language and cultural barriers during cross-language
communication. There are lots of text and documents on different languages need
to translation every day. It would be impossible to translation the huge amount
of data generated manually. Nowadays, there are lots of machine translation
tools are available in the world, such as Google translation, Bing translation,
Yandex, Baidu translation and Youdao translation and so on. Machine translation
services has been becoming more and more widely used, also more and more
popular. It is necessary for global integration to use Cross-language machine
translation tools. In especial, machine translation system has significantly
increased international trade \cite{brynjolfsson2018does}. Most research only
focuses on ranking the quantity of machine translation services in some field
\cite{pesu2018monte, aiken2010efficacy, koehn2006manual, somers2005round,
  shigenobu2007evaluation} but little research has conducted on difficult
translation text evaluation. In this paper, all of testing data (Origin Chinese
dataset) from DOUBAN, which is an Social Media website about books, movies,
music, to study the translation quality of different translation tools.
Douban film is China's largest and most authoritative
film sharing and comment community \cite{Douban}.
Social Media has been becoming more and more widely used.
Accounting to Perrin’s survey, there are only $7%$ American adults are use
social media in 2005. However, social media usage increase rapidly, there are
$65%$ American adults are use social media until 2015 \cite{perrin2015social}.
Social Media website comment text from the language word level has its unique
style, such as the text has colloquial vocabulary for the convenience of
expression. At present, it is urgent to carry out in-depth study
on this field, which may open up the new field of theoretical research.
In this study, we only fouced on three of Machine Translation tools, which are
Google, Yandex and Baidu.
Google translation tool come from American, Yandex come from Russia, and Baidu
come from China. This three tools all come from the top three powerful country.
Accounting to Pesu said machine translation tools can product better results on
European languages compare with Asian language \cite{pesu2018monte}. So, form
Chinese to English translation tool is the main kind of translation languages to
analysis translation difficults in the paper. Evaluation of machine translation
services difficults usually need language expert, who need well-known both languages, to
participate. However, language expert also involves human emotional judgment.
Automatic assessment human language is naturally difficult because of without a
test oracle \cite{zhou2016metamorphic}. In this paper, achieving a testing modle to automatic
assessment without language expert. Metamorphic testing(MT) is one of
property-based software quality testing method, which alreadly be appoved
effective for addressing the oracle problem, such as testing the quality of
search engine and the quality of Unmanned Aerial Vehicle(UAV) flight control
application and so on. Therefore, decideing metamorphic testing to find machine
translation services difficults in non-oracle sitation. And more specifically,
this research raise two questions.

@@

\subsection{Test Sample}
All of test sample came from Douban\footnote{Douban Website:
  https://www.douban.com/}, one of biggest social networking service
platforms in China. This social website attracts more than one hundred million
active visitors per month, and has amassed over sixty-five million registered
users \cite{doubanStat}. We then employ the Douban public Application Programming Interfaces
(APIs) to access Chinses-written comments. A typical data structure of harvested
comment is shown as a tuple: [Rating, Raw comments]. Totally, comments have got
46180 in the corpus. User rating total have 5 groups, which are 10, 20, 30, 40
and 50, from negative to positive.
The test sample distribution diagram on below.
\begin{figure}[h]
  \centering
\includegraphics[width=0.3\paperwidth]{./img/ratingHis.png}
\caption{User Rating Histogram}
\label{fig:userRatingHistogram}
\end{figure}
As you can see, the majority of comments allocate on rating 30. In addition,
there have got more negative comments compare with positive comments.

@@

\begin{enumerate}
  \item using three of machine translation services to translate Chinese
    original movie comments to English translated movie comments.
    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Google Translation)}$$
    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Yandex Translation)}$$
    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Baidu Translation)}$$
  \item Using Google sentiment analysis tool to analysis $P_{(Origin Data)}$,
    $P^{\prime}_{(Google Translation)}$, $ P^{\prime}_{(Yandex Translation)}$ and $
    P^{\prime}_{(Baidu Translation)}$. Google sentiment analysis APIs will get 2
    values, which are Score and Manitude. The range of Score is between -1 and
    1. If Score more close to 1 means this movie comment more positive, as well
    as, if Score more close to -1 means this movie comment more negative. In
    this paper, we have not analysis Manitude, which for distinction mix and neutral.
  \item\label{itm:testingProcedure3} Using user rating values (10, 20, 30, 40 or 50) to check Google
    Sentiment Analysis(SA) results $P_{(Origin Data)} $ is True or False. For
    example, user rating = 10 and Google Chinese SA score between -1
    and -0.6 (mean True) user ranking = 10 and Google Chinese SA score bigger
    than -0.6 (mean False). The decideing True table on below.\\
     \begin{table}[h]
      \caption {The Range of Score: True/ False}
     \begin{center}
      \begin{tabular}{|c|c|c|c|}
        \hline
        user rating & Google SA score & True/False \\
        \hline\hline
        10 & $[ \, -1, -0.4 ] \,$ & True \\
        \hline
        20 & $[ \, -0.8, 0 ] \,$ & True \\
        \hline
        30 & $[ \, -0.4, 0.4 ] \,$ & True \\
        \hline
        40 & $[ \, 0, 0.8 ] \,$ & True \\
        \hline
        50 & $[ \, 0.4, 1 ] \,$ & True \\
        \hline \hline
        10 & $( \, -0.4, 1 ] \,$ & False \\
        \hline
        20 & $[ \, -1, -0.8) \,$ & False \\
        \hline
        20 & $( \, -0.8, 1] \,$ & False \\
        \hline
        30 & $[ \, -1, -0.4) \,$ & False \\
        \hline
        30 & $( \, 0.4, 1] \,$ & False \\
        \hline
        40 & $[ \, -1, 0) \,$ & False \\
        \hline
        40 & $( \, 0.8, 1] \,$ & False \\
        \hline
        50 & $[ \, -1, 0.4) \,$ & False \\
        \hline
        \hline
      \end{tabular}
    \end{center}
  \end{table}

@@

\subsection{Grammatical Errors}
The machine translation have got lots of grammatical mistake, such as sequence
disorder, improper location of adverbial attributive. The subject, the
predicate, the attributive, the adverbial, and the object is incomplete, etc.
\subsubsection{Illogical connect}
\begin{itemize}
\item Chinese \underline{Origin Movie comment} is:
  \begin{center}
    ``明明是搞笑片最后弄成了教育片''
  \end{center}
\item The \underline{correct of the translation} is:\\
  ``Obviously it is a comedy,but it made into educational films finally''
\item The \underline{Baidu Translation} is:\\
  ``It's a funny movie that finally makes an education film''
\end{itemize}
The ``that'' is illogical to connect Subject part and subordinate clause.
\subsubsection{Incomplete ingredients}
Origin Chinese sentence is ``中间确实无聊得很，但是结尾不赖''. The original
sentence meaning ``It's really boring in the middle part, but it's not bad at
the end''. The Yandex Translation ``The middle of really boring very, however at the end''.
\subsubsection{Sequence Disorder}
``想过是烂片，只是没想到能烂到这种地步，太应付了，一个星期拍完的吧''
Google
``Think of a bad movie, but did not expect to be able to rot to this point, too
coping, a week finished it''
Yandex
``Thought is a bad film, just didn't think it could be rotten to the point where
too cope with, a week finished.''
baidu
``That is a bad film, but did not expect to come to this rotten, too for a week, finished.''

The problem of sentence structure.Incomplete sentence composition, confusion of
words order.

For example, original sentence meaning”A few small cups of grape
juice, it is not very fresh”.GoogleTranslation ”A few small cups of grape juice,
very fresh”in completely different meaning;

Take another example,original
sentence meaning “ The first story is good, but the other is too
contrived”.
YandexTranslation”On the first story good the other is too
contrived”;

Besides,For example,original sentence meaning “The first half was
good with heavy irony, but the last apology was a little
redundant”.

BaiduTranslation”The first half was good - the irony was very heavy,
and the last apology was a little redundant”. Improper location of clauses”-”.
The misuse of conjunctions”and”.

The problem of sentence structure.Causality is unclear. For example,original
sentence meaning "I can not ignorant conscience to give too few stars,because I
am a gentle person”.GoogleTranslation "I am a gentle person, and I really do not
have the heart to give too few stars. . .”

Take another example,original sentence meaning “Bad,I will never see Feng
Xiaogang's movie again.”  YandexTranslation “Sucks, feel Feng Xiaogang movie
later never to see.”

从以上以豆瓣电影评论为分析对象来讨论这三个翻译软件的译文共同的问题，从整体上看，
无论是用词还是语法都一定的错误导致许多译文意思不准确，内容残缺，结构错误。

 From the overall points of view, above the Douban film review as the analysis
 object to discuss GoogleTranslation, YandexTranslation and BaiduTranslation
 tools common problems, whether the usage of words or grammar are a certain
 error caused by many translation inaccurate meaning, incomplete content, and
 the wrong structure.

 The reasons are colloquial language characters of Douban film review text and
 insufficient machine vocabulary.Although the length of the movie commentary
 sentences is short, the vocabulary is not difficult and the sentences’structure
 seems simple, there have got lots of colloquial speech and many of words are
 not formal, which is the main reason for the low quality of translation
 results. Lots of compound sentence is hidded. It is more difficult for
 intelligent machines translation services.Although the length of the movie
 commentary sentences is short, the vocabulary is not difficult and the
 sentences’structure seems simple, there have got lots of colloquial speech and
 many of words are not formal, which is the main reason for the low quality of
 translation results. Lots of compound sentence is hidded. It is more difficult
 for intelligent machines translation services.

 Although the length of the movie commentary sentences is short, the vocabulary
is not difficult and the sentences' structure seems simple, there have got
lots of colloquial speech and many of words are not formal, which is the main
reason for the low quality of translation results. Lots of compound
sentence is hidded. It is more difficult for intelligent machines translation
services.

Although the online translation text comments and review is short in length, but
more colloquial is serious, the use of words is not standard, so vocabulary
translation is more difficult.Although the sentence structure seems simple, but
hides the compound sentence, but the sentence pattern is rich and
complex.Besides,Differences in thinking between Chinese and English is more
difficult for intelligent machines, which is the main difficulty in the quality
difficulties of translation

>>>>

\section{Introduction}
Most people encounter language and cultural barriers during cross-language
communication. There are lots of text and documents on different languages need
to translation every day. It would be impossible to translation the huge amount
of data generated manually. Nowadays, there are lots of machine translation
tools are available in the world, such as Google translation, Bing translation,
Yandex, Baidu translation and Youdao translation and so on. Machine translation
services has been becoming more and more widely used, also more and more
popular. It is necessary for global integration to use Cross-language machine
translation tools. In especial, machine translation system has significantly
increased international trade \cite{brynjolfsson2018does}. Most research only
focuses on ranking the quantity of machine translation services in some field
\cite{pesu2018monte, aiken2010efficacy, koehn2006manual, somers2005round,
  shigenobu2007evaluation} but little research has conducted on difficult
translation text evaluation. In this paper, all of testing data (Origin Chinese
dataset) from DOUBAN, which is an Social Media website about books, movies,
music, to study the translation quality of different translation tools.
Douban film is China's largest and most authoritative
film sharing and comment community \cite{Douban}.
Social Media has been becoming more and more widely used.
Accounting to Perrin's survey, there are only $7\%$ of American adults are use
social media in 2005. However, social media usage increase rapidly, there are
$65\%$ American adults are use social media until 2015 \cite{perrin2015}.
Social Media website comment text from the language word level has its unique
style, such as the text has colloquial vocabulary for the convenience of
expression. At present, it is urgent to carry out in-depth study
on this field, which may open up the new field of theoretical research.
In this study, we only fouced on three of Machine Translation tools, which are
Google, Yandex and Baidu.
Google translation tool come from American, Yandex come from Russia, and Baidu
come from China. This three tools all come from the top three powerful country.
Accounting to Pesu said machine translation tools can product better results on
European languages compare with Asian language \cite{pesu2018monte}. So, form
Chinese to English translation tool is the main kind of translation languages to
analysis translation difficults in the paper. Evaluation of machine translation
services difficults usually need language expert, who need well-known both languages, to
participate. However, language expert also involves human emotional judgment.
Automatic assessment human language is naturally difficult because of without a
test oracle \cite{zhou2016metamorphic}. In this paper, achieving a testing modle to automatic
assessment without language expert. Metamorphic testing(MT) is one of
property-based software quality testing method, which alreadly be appoved
effective for addressing the oracle problem, such as testing the quality of
search engine and the quality of Unmanned Aerial Vehicle(UAV) flight control
application and so on. Therefore, decideing metamorphic testing to find machine
translation services difficults in non-oracle sitation. And more specifically,
this research raise two questions.

@@

\subsection{Test Sample}
All of test sample came from Douban\footnote{Douban Website:
  https://www.douban.com/}, one of biggest social networking service
platforms in China. This social website attracts more than one hundred million
active visitors per month, and has amassed over sixty-five million registered
users \cite{doubanStat}. We then employ the Douban public Application Programming Interfaces
(APIs) to access Chinses-written comments. A typical data structure of harvested
comment is shown as a tuple: [Rating, Raw comments]. Totally, comments have got
46180 in the corpus. User rating total have 5 groups, which are 10, 20, 30, 40
and 50, from negative to positive.
The test sample distribution diagram on below.\\
\begin{wrapfigure}
  \centering
  \includegraphics[width=0.3\paperwidth]{./img/ratingHis.png}
  \label{fig:userRatingHistogram}
\end{wrapfigure}\\

As you can see, the majority of comments allocate on rating 30. In addition,
there have got more negative comments compare with positive comments.

@@

\begin{enumerate}
  \item using three of machine translation services to translate Chinese
    original movie comments to English translated movie comments.
    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Google Translation)}$$
    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Yandex Translation)}$$
    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Baidu Translation)}$$
  \item Using Google sentiment analysis tool to analysis $P_{(Origin Data)}$,
    $P^{\prime}_{(Google Translation)}$, $ P^{\prime}_{(Yandex Translation)}$ and $
    P^{\prime}_{(Baidu Translation)}$. Google sentiment analysis APIs will get 2
    values, which are Score and Manitude. The range of Score is between -1 and
    1. If Score more close to 1 means this movie comment more positive, as well
    as, if Score more close to -1 means this movie comment more negative. In
    this paper, we have not analysis Manitude, which for distinction mix and neutral.
  \item\label{itm:testingProcedure3} Using user rating values (10, 20, 30, 40 or 50) to check Google
    Sentiment Analysis(SA) results $P_{(Origin Data)} $ is True or False. For
    example, user rating = 10 and Google Chinese SA score between -1
    and -0.6 (mean True) user ranking = 10 and Google Chinese SA score bigger
    than -0.6 (mean False). The decideing True table on below.\\
     \begin{table}[h!]
      \caption {The Range of Score: True/ False}
     \begin{center}
      \begin{tabular}{|c|c|c|c|}
        \hline
        user rating & Google SA score & True/False \\
        \hline\hline
        10 & $[ \, -1, -0.4 ] \,$ & True \\
        \hline
        20 & $[ \, -0.8, 0 ] \,$ & True \\
        \hline
        30 & $[ \, -0.4, 0.4 ] \,$ & True \\
        \hline
        40 & $[ \, 0, 0.8 ] \,$ & True \\
        \hline
        50 & $[ \, 0.4, 1 ] \,$ & True \\
        \hline \hline
        10 & $( \, -0.4, 1 ] \,$ & False \\
        \hline
        20 & $[ \, -1, -0.8) \,$ & False \\
        \hline
        20 & $( \, -0.8, 1] \,$ & False \\
        \hline
        30 & $[ \, -1, -0.4) \,$ & False \\
        \hline
        30 & $( \, 0.4, 1] \,$ & False \\
        \hline
        40 & $[ \, -1, 0) \,$ & False \\
        \hline
        40 & $( \, 0.8, 1] \,$ & False \\
        \hline
        50 & $[ \, -1, 0.4) \,$ & False \\
        \hline
        \hline
      \end{tabular}
    \end{center}
  \end{table}

@@

\subsection{Grammatical Errors}
The machine translation have got lots of grammatical mistake, such as sequence
disorder, improper location of adverbial attributive. The subject, the
predicate, the attributive, the adverbial, and the object is incomplete, etc.
\subsubsection{Illogical connect}
\begin{itemize}
\item Chinese \underline{Origin Movie comment} is:
  \begin{center}
    ``明明是搞笑片最后弄成了教育片''
  \end{center}
\item The \underline{correct of the translation} is:\\
  ``Obviously it is a comedy,but it made into educational films finally''
\item The \underline{Baidu Translation} is:\\
  ``It's a funny movie that finally makes an education film''
\end{itemize}
The ``that'' is illogical to connect Subject part and subordinate clause.
\subsubsection{Incomplete ingredients}
Origin Chinese sentence is ``中间确实无聊得很，但是结尾不赖''. The original
sentence meaning ``It's really boring in the middle part, but it's not bad at
the end''. The Yandex Translation ``The middle of really boring very, however at the end''.
\subsubsection{Sequence Disorder}
\begin{itemize}
\item Chinese \underline{Origin Movie comment} is:
  \begin{center}
    ``想过是烂片，只是没想到能烂到这种地步，太应付了，一个星期拍完的吧''
  \end{center}
\item The \underline{correct of the translation} is:\\
  ``I was have thought this is worse movie, but did not think it could be worse
  like this. It's working perfunctorily. Is it only using one week to finish all?''
\item The \underline{Google Translation} is:\\
  ``Think of a bad movie, but did not expect to be able to rot to this point,
  too coping, a week finished it''
\item The \underline{Yandex Translation} is:\\
  ``Thought is a bad film, just didn't think it could be rotten to the point where
too cope with, a week finished.''
\item The \underline{Baidu Translation} is:\\
  ``That is a bad film, but did not expect to come to this rotten, too for a week, finished.''
\end{itemize}
This is not only have professional terms word translation problem. This
translation have incomplete sentence composition and confusion of words order.

From the overall points of view, above of movie comments as the analysis
object to discuss Google Translation, Yandex Translation and Baidu Translation
tools have got common problems. The usage of words or grammar are a certain
error caused by many translation inaccurate meaning, incomplete content, and
the wrong structure.

The reasons are colloquial language characters of Douban film review comments and
insufficient machine translation vocabulary collection library. Although the
online translation text comments and review is short in length, but
more colloquial is serious, the use of words is not standard, so vocabulary
translation is more difficult. Although the sentence structure seems simple, but
hides the compound sentence, but the sentence pattern is rich and
complex. Besides,Differences in thinking between Chinese and English is more
difficult for intelligent machines, which is the main difficulty in the quality
difficulties of translation
